\speculake: Hiding Malware in Speculative Execution

### 2018-04-30 paper/payloads.tex
add aes description

\subsection{Unpacking and Decryption}
\label{subsec:decryption}
- AES instructions

>>>>

\subsection{Unpacking and Decryption}
\label{subsec:decryption}
While Section \ref{subsec:turing} demonstrates that arbitary computation is
possible, if a reverse engineer can discover the \emph{speculative instructions}
they can determine the execution of this program by simply reading the
instructions that are passed along. To avoid this we can encrypt the
\emph{speculative instructions}, meaning that a reverse engineer can never
determine these instructions by examining the ELF file, or generating source
code.

The encrypted code must be decrypted so that the instructions can be executed.
In order to obscure this information from the ``real world'' the speculative
world must do the decryption. As such we have built a prototype capable of
decrypting messages in the speculative world and passing the results back to the
real world in pieces.

The speculative world is able to take advantage of the AES-NI instructions to
decrypt messages. In order to avoid detection (as well as reduce the computation
that needs to be done in the speculative world) the key expansion can be done
ahead of time. However, the key schedule does have a structure that could be
detected by a reverse engineer. Thus 11 random round keys are selected. This
obfuscated key schedule makes it more difficult for a reverse engineer to
determine that there is encrypted content. Additionally since the content is
only accessed when the correct trigger program is running the challenges facing
a reverse engineer are great.
